
---
title: "Analysis CTC - area 2"
author: "Maiara Pusch"
---


The variables created throughout the code have been stored and can be loaded directly by the chunck below.
```{r}
#load("RData/analise.CTC.ipiranga.RData")
```

installation of packages
```{r}
#install.packages("pacman")
pacman::p_load(georob, dplyr, tidyverse,pedometrics,raster,gstat,googlesheets,mapview,corrr,sf,robustbase,reshape,MASS,ggplot2,colormap,rgdal,caret,car)
```

Reading soil data
```{r}
dados = read.csv("../Data/Soil/data_CTC.csv")
dados=na.omit(dados)
names(dados)
```

Before the analyses, the variables that would be used were selected from the data set, being:
```{r}
dados= dados %>% dplyr::select(x, y, CTC)
```  


When working with the integer values of the coordinates, the model displays errors in converting the values. In this way, subtract scans from the coordinates of their respective minimum values.

```{r}
dados$coordx= dados$x - min(dados$x)
dados$coordy= dados$y - min(dados$y)
```

Viewing points and area
```{r}
poly= shapefile("../Data/Boundary/22S.shp")
coordinates(dados)= ~x+y
crs(dados)= crs(poly)
#spplot(dat, zcol="CTC") 
mapview(poly, alpha.regions = 0.01, color = "red", map.types = c("Esri.WorldImagery")) + mapview(dados, zcol="CTC", legend=T)
```

```{r}
par(mfcol=c(2,2))
boxplot(dados$CTC, horizontal=TRUE, outline=TRUE)
hist(dados$CTC, col= "gray", xlab="CTC", main=" CTC")
#hist(log(dados$CTC), col= "gray", xlab="Potássio", main="log(CTC)")
#qqnorm(dados$CTC)
```

 Reading the covariable in raster and visualization 
```{r}
variaveis_auxiliares = list.files(path = "../Data/Covariates/", pattern = ".tif$", full.names = T)
# Convert list to stack
variaveis_auxiliares <- raster::stack(variaveis_auxiliares)
plot(variaveis_auxiliares, maxnl=20, nc=5)
```

Extraction of auxiliary information co-located with soil sampling points
```{r}
# extrair da lista de acordo com os pontos de solo
dat = raster::extract(variaveis_auxiliares, dados)
dados = cbind(dados, dat)
```

Soil types were grouped according to the third classification (Santos et al., 2013), thus grouping into 3 classes: 1.2 and 3- it´s only showed the classes
```{r}
tiposdesolo= shapefile("../Data/Types_of_soil/tipos_solo_22_S.shp")

mapview(tiposdesolo) 
```

In parentheses are the numbers corresponding to the soil classes.

*LVAe2.1(**6**), LVe1.1(**2**) e LVef1.1(**1**) received the number 10.

* PVAa3.1(**7**), LVAd3.1(**8**), LVAd2.1(**3**), LVAa3.1(**5**) received the number 20.

* RQoa4.1(**4**) e RQod4.1(**9**) received the number 30.
```{r}
dados$TPS[dados$TPS=="1"]=10
dados$TPS[dados$TPS=="2"]=10
dados$TPS[dados$TPS== "6"]=10
dados$TPS[dados$TPS== "7"]=20
dados$TPS[dados$TPS== "8"]=20
dados$TPS[dados$TPS== "3"]=20
dados$TPS[dados$TPS== "5"]=20
dados$TPS[dados$TPS=="4"]=30
dados$TPS[dados$TPS=="9"]=30
dados$TPS= as.factor(dados$TPS)
dados$talhoes= as.factor(dados$talhoes)
dados=na.omit(dados)
str(dados)
```


 Check the relationship of soil types with CTC
```{r}
np= plyr::count(dados$TPS)

ggplot(as.data.frame(dados), aes(TPS, CTC)) +
   ylab("CTC (mmolc dm-3)")+
  xlab("TPS")+
  geom_boxplot(outlier.colour = "red") + 
  annotate("text",x=np$x, y=120, label = np$freq, colour= "red", size=4.5)+
theme_bw(base_size = 15)
``` 

Check the relationship of the butchers with the  CTC
```{r}
np= plyr::count(dados$talhoes)

ggplot(as.data.frame(dados), aes(talhoes, CTC)) +
  ylab("CTC (mmolc dm-3)")+
  xlab("Fields")+
  geom_boxplot(outlier.colour = "red") + 
  annotate("text",x=np$x, y=120, label = np$freq, colour= "red", size=4.5)+
theme_bw(base_size = 15)
``` 

correlation between variables
```{r}
cor= dados %>%
  as.data.frame() %>%
  dplyr::select(- TPS, - talhoes, - coordx, - coordy)%>%
  correlate(method = "spearman", diagonal = 1, use = "pairwise.complete.obs")%>%
  mutate_if(is.numeric, round, 3) %>% 
   as.data.frame()
cor
```
 
Variables that had correlations greater than **0.9** were selected  
```{r}
cor_above = cor %>%  
  gather(-term, key = "colname", value = "cor") %>% 
  filter(abs(cor) < 1 & abs(cor) >= 0.9) %>% 
  dplyr::select(term, colname, cor) %>% 
  distinct(cor, term,colname) %>% 
  arrange(cor) 
cor_above
```  

```{r}
names_above = cor_above$term
names_above
selected_var = cor %>% 
  dplyr::select(CTC, term) %>% 
  filter(term %in% names_above) %>% 
  arrange(CTC)
selected_var
```

```{r}
reg.cov <- lm(CTC ~ ., data = dplyr::select(as.data.frame(dados), -b3,-b4,-b5, -catch_area, -sw1, -sw2, - CH_0.5m, - coordx, -coordy))

reg.cov.vif <- pedometrics::stepVIF(reg.cov, threshold = 10)
```

```{r}
summary(reg.cov.vif)
```

visualization of the behavior of multiple regression residuals as a function of the variables without colinearitye

```{r}
par(mfrow=c(2,2))
plot(reg.cov.vif, which=c(1:6))
hist(reg.cov.vif$residuals)
boxplot(reg.cov.vif$residuals, horizontal = T)
# dw= dwtest(CTC ~ CH_1 + slope + SPI + talhoes + TWI + y, data = as.data.frame(dados))
# dw
```

Selection of auxiliary variables by AKAIKE criterion (AIC)
```{r}
reg.aic= MASS::stepAIC(reg.cov.vif)
```

```{r}
summary(reg.aic)
```

### Adjustment of the multivariate model according to auxiliary variables 
```{r}
min(dist(dados@coords))
```

```{r}
plot(ku.sv <-sample.variogram(residuals(reg.aic),locations = dados@coords, lag.dist.def= seq(0,1200, by=100), estimador="qn"), type="p", annotate=T, main="Resíduos da regressão");grid()
```


```{r}
ku= georob::georob(CTC ~ CH_1 + slope + SPI + talhoes + TWI + coordy, data = dados,  locations = ~ x + y,variogram.model = "RMmatern", param=c(variance=200, nugget=110, scale= 350, nu=1.5), fit.param = default.fit.param(variance=T, nugget = T, scale=T, nu=F), psi.func = c("huber"))

ku.sph= georob::georob(CTC ~ CH_1 + slope + SPI + talhoes + TWI + coordy, data = dados,  locations = ~ x + y,variogram.model = "RMspheric", param=c(variance=200, nugget=110, scale= 350), fit.param = default.fit.param(variance=T, nugget = T, scale=T), psi.func = c("huber"))

ku.exp= georob::georob(CTC ~ CH_1 + slope + SPI + talhoes + TWI + coordy, data = dados,  locations = ~ x + y,variogram.model = "RMexp", param=c(variance=200, nugget=110, scale= 350), fit.param = default.fit.param(variance=T, nugget = T, scale=T), psi.func = c("huber"))
```

```{r}
summary(ku)
```

Does not converge 
```{r}
#summary(ku.sph)
```

Does not converge 
```{r}
#summary(ku.exp)
```

```{r }
# prfl.ku <- profilelogLik(ku ,values=data.frame(scale=seq(100, 800, by=25)))
# plot(loglik~scale, prfl.ku, type="l", main="ku")
```

Cross-validation (LOOCV)
```{r}
cv.ku = georob::cv(ku, seed= 42, nset = 95, ncores=6)
#cv.ku.exp =georob::cv(ku.exp, seed= 42, nset =95, ncores=6)
```

```{r}
cv.ku
```

```{r}
plot(cv.ku, main="Matern")
#plot(cv.ku.exp, main="Exponential")
#plot(cv.ku.sph, main="Spheric")
```

```{r}
plot(ku, lag.dist.def=seq(0,1000, by=100), max.lag=1100, estimator="qn", xlab ="Distance", ylab = "Semivariance", main="ku", type="p",annotate=T)
#lines(ku.sph, col="red")
#lines(ku.exp, col="blue")
```

### Adjustment of the multivariate model according to coordinates 
```{r}
reg.xy= lm(CTC ~ coordx + coordy, dados)
plot(ku.sv <-sample.variogram(residuals(reg.xy),locations = dados@coords, lag.dist.def= seq(0,600, by=60), estimador="qn"), type="p", annotate=T)
```

```{r}
ku.xy = georob::georob(CTC ~ coordx + coordy, data = dados,  locations = ~ x + y, variogram.model = "RMmatern", param=c(variance=300, nugget=100, scale= 400, nu=0.5), fit.param = default.fit.param(variance=T, nugget = T, scale=T, nu=F), psi.func = c("huber"), verbose=1)

ku.xy.sph = georob::georob(CTC ~ coordx + coordy, data = dados,  locations = ~ x + y, variogram.model = "RMspheric", param=c(variance=300, nugget=100, scale= 400), fit.param = default.fit.param(variance=T, nugget = T, scale=T),psi.func = c("huber"), verbose=1)

ku.xy.exp = georob::georob(CTC ~ coordx + coordy, data = dados,  locations = ~ x + y, variogram.model = "RMexp", param=c(variance=300, nugget=100, scale= 400), fit.param = default.fit.param(variance=T, nugget = T, scale=T),psi.func = c("huber"), verbose=1)
```

```{r}
summary(ku.xy)
```
```{r}
summary(ku.xy.sph)
```
```{r}
summary(ku.xy.exp)
```

Cross-validation 
```{r}
cv.xy = georob::cv(ku.xy, seed= 42, nset =95, ncores=6,  control=control.georob(initial.param=FALSE))
cv.xy.sph = georob::cv(ku.xy.sph, seed= 42, nset =95, ncores=6,control=control.georob(initial.param=FALSE))
cv.xy.exp = georob::cv(ku.xy.exp, seed= 42, nset =95, ncores=6,control=control.georob(initial.param=FALSE))
```

```{r}
cv.xy;cv.xy.sph;cv.xy.exp
```


```{r}
# plot(cv.xy, main="Matern")
# plot(cv.xy.sph, main="Spheric")
# plot(cv.xy.exp, main="Exponential")
```

```{r}
print(plot(ku.xy, lag.dist.def= seq(0,800, by=100), max.lag=2000, estimator="qn", xlab ="Distance", ylab = "Semivariance", type="p",annotate=T, main="ku ~xy"))
#lines(ku.xy.exp, col="red")
#lines(ku.xy.sph, col="blue")
```

### Univariate model adjustment

```{r} 
reg.kri= lm(CTC ~1, dados)
plot(kri.sv <-sample.variogram(residuals(reg.kri),locations = dados@coords, lag.dist.def= seq(0,800, by=100), estimador="qn"), type="p", annotate=T)
```

```{r}
kri=  georob::georob(CTC ~ 1, data = dados,  locations = ~ x + y,variogram.model = "RMmatern",param=c(variance=300, nugget=100, scale= 450, nu= 1.5), fit.param = default.fit.param(variance=T, nugget = T, scale=T, nu=F),psi.func = c("huber"))

kri.sph=  georob::georob(CTC ~ 1, data = dados,  locations = ~ x + y,variogram.model = "RMsph",param=c(variance=300, nugget=100, scale= 450), fit.param = default.fit.param(variance=T, nugget = T, scale=T),psi.func = c("huber"))

kri.exp=  georob::georob(CTC ~ 1, data = dados,  locations = ~ x + y,variogram.model = "RMexp",param=c(variance=300, nugget=100, scale= 450), fit.param = default.fit.param(variance=T, nugget = T, scale=T),psi.func = c("huber"))
```

```{r}
summary(kri)
```

```{r}
summary(kri.sph)
```

does not converge  
```{r}
summary(kri.exp)
```

```{r}
print(plot(kri, lag.dist.def=seq(0,600, by=100), max.lag=1100, estimator="qn", xlab ="Distance", ylab = "Semivariance", type="p",annotate=T, main="kriging"))
lines(kri.sph, col="red")
#lines(kri.exp, col = "blue")
```

Cross-validation (LOOCV)
```{r}
cv.kri = georob::cv(kri, seed= 42, nset =95, ncores=6,control=control.georob(initial.param=FALSE))
cv.kri.sph = georob::cv(kri.sph, seed= 42, nset =95, ncores=6,control=control.georob(initial.param=FALSE))
#cv.kri.exp = georob::cv(kri.exp, seed= 42, nset =95, ncores=6,control=control.georob(initial.param=FALSE))
```

```{r}
cv.kri;cv.kri.sph
```

```{r}
# plot(cv.kri, main="Matern")
# plot(cv.kri.sph, main="Spheric")
# plot(cv.kri.exp, main="Exponential")
```


Visualization of semivariogram all models
```{r}
print(plot(kri, lag.dist.def=seq(0,600, by=100), estimator="qn", xlab ="Distance", ylab = "Semivariance", type="p",cex.lab=1.5, cex.axis=1.5));grid()
print(plot(ku.xy, lag.dist.def=seq(0,00, by=100), estimator="qn", xlab ="Distance", ylab = "Semivariance", type="p",add=T, col="blue", cex.lab=1.5, cex.axis=1.5))
print(plot(ku, lag.dist.def=seq(0,600, by=100),  estimator="qn", xlab ="Distance", ylab = "Semivariance", type="p",add=T, col="red", cex.lab=1.5, cex.axis=1.5))
title("CTC (mmolc dm-3) - Area 2")
legend("bottomright", lt=1, col=c("black", "blue", "magenta"), legend = c("Robust Ordinary Kriging", "Robust Universal Kriging ~ x + y", "Robust Universal Kriging ~ cov"))
```

Cross-validation (LOOCV) deterministic model IDW 
```{r}
cv.idw=gstat::krige.cv(CTC ~ 1, dados, nfold = 96)# validação cruzada
cv.idw=as.data.frame(cv.idw)# transforma para data.frame
statistics.idw <- c(
        me = mean(cv.idw$observed - cv.idw$var1.pred),
        medme = median(cv.idw$observed - cv.idw$var1.pred),
        mae = mean(abs(cv.idw$observed - cv.idw$var1.pred)),
        rmse = sqrt( mean((cv.idw$observed - cv.idw$var1.pred )^2 ) ),
        nse2 =1- sum((cv.idw$observed - cv.idw$var1.pred)^2)/ sum((cv.idw$observed- mean(cv.idw$observed))^2),
        nse1 =1- sum(abs(cv.idw$observed - cv.idw$var1.pred))/ sum(abs(cv.idw$observed- mean(cv.idw$observed))))
```

```{r}
# plot(cv.idw$observed ~cv.idw$var1.pred)
# lmidw=lm(cv.idw$observed ~cv.idw$var1.pred)
# abline(lmidw)
```

Cross-validation (LOOCV) for the regression model according to auxiliary variables

* The dat variable was added, only the information used in cross-validation, in order to facilitate calculations.
* A data frame was created that would store the metrics
* The average of the metrics of each fold was performed

```{r}
dat = dplyr::select(as.data.frame(dados), 
   -b3, -b4, -b5, -catch_area, -sw1, -sw2, -CH_0.5m, -coordx)
```


```{r}
model= MASS::rlm(CTC ~ CH_1 + slope + SPI + talhoes + 
    TWI + coordy, data=dat, psi = psi.huber, k2= 2, escale.est= "Huber")

#data <- model.frame(model)
idx  <- seq(1, nrow(dat), 1)
#data <- cbind(data, idx)
obs  <- numeric()
pred <- numeric()
pev  <- numeric()
    # run cross-validation
for (i in 1:nrow(dat)) {
      cv.fit     <- MASS::rlm(formula(model), subset = idx[-i], data = dat, psi = psi.huber, k=2, escale.est= "Huber")
      cv.pred    <- predict(cv.fit, dat[i, ], se.fit = TRUE, interval =c("prediction"), type= c("response"))
      obs[i]     <- dat[i, 1]
      pred[i]    <- cv.pred$fit
  
      # standard deviation of the predicted mean value of Y
      # sd.mean[i] <- cv.pred$se.fit
      # standard deviation of a predicted values of an individual observation
      # also known as prediction error variance
      pev[i] <- (sqrt(1 + c(cv.pred$se.fit/cv.pred$residual.scale) ^ 2) *
                   cv.pred$residual.scale) ^ 2
}

pev2= (cv.pred$se.fit^2) + (cv.pred$residual.scale^2)

statistics.predict <- c(
        me = mean(obs - pred),
        
        medme = median(obs - pred), 
        
        mae = mean(abs(obs - pred)),
        
        rmse = sqrt(mean((obs - pred)^2)),
        
        nse2 =1-sum((obs - pred)^2)/
        sum((obs - mean(obs))^2),

        nse1 =1-(sum(abs(obs - pred))/
        sum(abs(obs - mean(obs)))),
        # Compara as diferenças do erro ao quadrado pela variação dos erros de predição    
        msdr =mean((obs - pred)^2/pev),
        
        medsse =median((obs - pred)^2/pev))

msdr2 =mean((obs - pred)^2/pev2)
statistics.predict
```

```{r}
# par(mfcol=c(2,2))
# boxplot(cv.fit$residuals, horizontal= T)
# hist(cv.fit$residuals, col="gray")
```

```{r}
#r2= hydroGOF::br2(cv.xy.exp$pred$pred,cv.xy.exp$pred$data)
```


```{r}
statistics.kri <- c(
        me = mean(cv.kri.sph$pred$data - cv.kri.sph$pred$pred),
        medme = median(cv.kri.sph$pred$data - cv.kri.sph$pred$pred),
        mae = mean(abs(cv.kri.sph$pred$data - cv.kri.sph$pred$pred)),
        rmse = sqrt(mean((cv.kri.sph$pred$data - cv.kri.sph$pred$pred)^2)),
        nse2=1-sum((cv.kri.sph$pred$data - cv.kri.sph$pred$pred)^2)/
        sum((cv.kri.sph$pred$data- mean(cv.kri.sph$pred$data))^2),
        nse1=1-sum(abs(cv.kri.sph$pred$data - cv.kri.sph$pred$pred))/
        sum(abs(cv.kri.sph$pred$data- mean(cv.kri.sph$pred$data))),
        msse= mean(((cv.kri.sph$pred$data - cv.kri.sph$pred$pred)/cv.kri.sph$pred$se)^2))
```


```{r}
statistics.xy <- c(
        me = mean(cv.xy.sph$pred$data - cv.xy.sph$pred$pred),
        medme = median(cv.xy.sph$pred$data - cv.xy.sph$pred$pred),
        mae = mean(abs(cv.xy.sph$pred$data - cv.xy.sph$pred$pred)),
        rmse = sqrt( mean((cv.xy.sph$pred$data - cv.xy.sph$pred$pred)^2)),
        nse2=1-sum((cv.xy.sph$pred$data - cv.xy.sph$pred$pred)^2)/
        sum((cv.xy.sph$pred$data- mean(cv.xy.sph$pred$data))^2),
        nse1=1-sum(abs(cv.xy.sph$pred$data - cv.xy.sph$pred$pred))/
        sum(abs(cv.xy.sph$pred$data- mean(cv.xy.sph$pred$data))),
        msse= mean(((cv.xy.sph$pred$data - cv.xy.sph$pred$pred)/cv.xy.sph$pred$se)^2))
```

```{r}
statistics.ku <- c(
        me = mean(cv.ku$pred$data - cv.ku$pred$pred),
        medme = median(cv.ku$pred$data - cv.ku$pred$pred),
        mae = mean(abs(cv.ku$pred$data - cv.ku$pred$pred)),
        rmse = sqrt(mean((cv.ku$pred$data - cv.ku$pred$pred)^2)),
        nse2=1-sum((cv.ku$pred$data - cv.ku$pred$pred)^2)/
        sum((cv.ku$pred$data- mean(cv.ku$pred$data))^2),
        nse1=1-sum(abs(cv.ku$pred$data - cv.ku$pred$pred))/
        sum(abs(cv.ku$pred$data- mean(cv.ku$pred$data))),
        msse= mean(((cv.ku$pred$data - cv.ku$pred$pred)/cv.ku$pred$se)^2))
```

```{r}
print(plot(kri, lag.dist.def=seq(0,600, by=100), max.lag=1100, estimator="qn", xlab ="Distance", ylab = "Semivariance", type="p", cex.lab=1.2, cex.axis=1.2))
print(plot(ku.xy, lag.dist.def=seq(0,600, by=100), max.lag=1100, estimator="qn", xlab ="Distance", ylab = "Semivariance", type="p" ,add=T, col="blue", cex.lab=1.2, cex.axis=1.2))
print(plot(ku, lag.dist.def=seq(0,600, by=100), max.lag=1100, estimator="qn", xlab ="Distance", ylab = "Semivariance", type="p",add=T, col="red", cex.lab=1.2, cex.axis=1.2))
legend("bottomright", lt=1, col=c("black", "blue", "red"), legend = c("Robust Ordinary Kriging", "Robust Universal Kriging ~ x + y", "Robust Universal Kriging ~ cov"), cex=1.2)
```

```{r}
me= rbind(statistics.kri, statistics.xy, statistics.ku)
statistics.idw;me;statistics.predict; 
me
```

```{r}
cv.kri;cv.xy;cv.ku
```

Extracting auxiliary information values for the entire interpolation grid node
```{r}
# rasterizo o contorno para  a resolução do mapa interpolado
boundary <-raster::shapefile("../Data/Boundary/22S.shp")
r =raster::raster(boundary, res = 10) # rerolu??o do pixel 
rp =raster::rasterize(boundary, r, 0) # cria um objeto no formato raster
grid = as(rp, "SpatialPixelsDataFrame") # transforma em pontos onde ser?o realizadas as interpola??es
pontos_grid= raster::extract(variaveis_auxiliares, grid)
# Combino os extraidos
grid_interpolacao = cbind(grid,pontos_grid)
grid_interpolacao = na.omit(grid_interpolacao)
```

Creation of the prediction grid
```{r}
grid_interpolacao$coordx= grid_interpolacao$x- min(grid_interpolacao$x)
grid_interpolacao$coordy= grid_interpolacao$y- min(grid_interpolacao$y)
grid_interpolacao$talhoes = as.factor(grid_interpolacao$talhoes)
```


prediction by KU according to auxiliary variables and visualization of the prediction map 
```{r}
map.ku.cov <- predict(ku, newdata= grid_interpolacao, control=control.predict.georob(extended.output=TRUE))
sp::gridded(map.ku.cov)= TRUE
sp::spplot(map.ku.cov, c("pred"), main="Robust Universal Kriging prediction", scales=list(draw=TRUE))
```

```{r}
round(cbind(dados@coords,rweights=ku[["rweights"]])[c(14,62,86),],2)
sel <- ku[["rweights"]] <= 0.8 & !1:nrow(dados) %in% c(14,62,86)
round(cbind(dados@coords,rweights=ku[["rweights"]])[sel,],2)
plot(poly)
points(y~x, dados, subset=c(45,92,96,14,62,86), pch=4); grid()
```

prediction by KU according to the coordinates and visualization of the prediction map
```{r }
map.ku.xy <- predict(ku.xy.sph, newdata= grid_interpolacao, control=control.predict.georob(extended.output=TRUE))
sp::gridded(map.ku.xy)= TRUE
sp::spplot(map.ku.xy, c("pred"), main="Robust Universal Kriging prediction", scales=list(draw=TRUE)) 
```

Prediction by OK and visualization of the prediction map 

```{r}
map.kri <- predict(kri.sph, newdata= grid_interpolacao, control=control.predict.georob(extended.output=TRUE))
sp::gridded(map.kri)= TRUE
sp::spplot(map.kri, c("pred"), main="Robust Ordinary Kriging prediction", scales=list(draw=TRUE))
```

Deterministic model prediction and prediction map visualization
```{r}
proj4string(dados)= CRS(proj4string(grid_interpolacao))
map.idw= gstat::idw(CTC ~ 1, dados, grid_interpolacao)
sp::spplot(map.idw, c("var1.pred"),main="IDW prediction", scales=list(draw=TRUE))
```


Prediction of the regression model and prediction map visualization
```{r}
grid.reg = as.data.frame(grid_interpolacao)
#grid.reg= na.omit(grid.reg)
map.reg =  predict(model, newdata= grid.reg, type = c("response"), se.fit=T)
map.reg = as.data.frame(map.reg)
map.reg$x = grid.reg$x
map.reg$y = grid.reg$y
map.reg
map.reg=dplyr::select(map.reg, x, y,fit, se.fit)
map.reg=rasterFromXYZ(map.reg)
sp::spplot(map.reg, c("fit"))
sp::spplot(map.reg, c("se.fit"))
```



Selects the predicted values of each method. Then we group in a data frame so that I calculate the densities, it is necessary that the memos are grouped into a single column, for this we use the melt function.

```{r}
ROK= (cv.kri$pred$pred)
RUK_coord= (cv.xy$pred$pred)
RUK_covars= na.omit(cv.ku$pred$pred)
IDW= (cv.idw$var1.pred)
RMLR= (pred)
OBS= dados$CTC
min(obs)
#df=cbind(kri.pred, obs,xy.pred)
df= cbind(IDW, RMLR, ROK, RUK_coord, RUK_covars, OBS)
df = as.data.frame(df)
df1=reshape::melt(df, variable.series = "Metodos")
df1 = dplyr::rename(df1, Methods= variable)
#write.csv(df1, "../dados/df1.ctc_ipiranga.csv")
```

Compare the similarity between two distributions by means of the kolmorogov-smirnov test
```{r}
# Kolmorogv-smirnov
obs.kri= ks.test(OBS, KRI)
#obs.kri1= kl.dist(OBS, KRI)
obs.ku= ks.test(OBS, KU)
#obs.ku1= kl.dist(OBS, KU)
obs.ku_xy= ks.test(OBS, KU_XY)
#obs.ku_xy1= kl.dist(OBS, KU_XY)
obs.idw= ks.test(OBS, IDW)
#obs.idw1= kl.dist(OBS, IDW)
obs.reg= ks.test(OBS, REG)
#obs.reg1= kl.dist(OBS, REG)


IDW.ks= obs.idw$statistic
KRI.ks = obs.kri$statistic
KU_XY.ks = obs.ku_xy$statistic
KU.ks = obs.ku$statistic
REG.ks = obs.reg$statistic
ks= cbind(IDW.ks,REG.ks, KRI.ks, KU_XY.ks, KU.ks)
ks= as.data.frame(ks)
ks= dplyr::rename(ks, IDW=IDW.ks, REG= REG.ks, KRI=KRI.ks, KU_XY=KU_XY.ks, KU= KU.ks)
t(ks)
```

Density of predicted values in cross-validation

```{r}
ggplot(df1, aes(x= value, y= Methods, fill= Methods) )+
  ggridges::geom_density_ridges(scale=3, alpha=1, show.legend = F)+
  labs(title = "CTC (mmolc dm-3) - Area 2") +
  scale_fill_manual(values=c("#440154FF", "#414487FF", "#2A788EFF", "#22A884FF", "#7AD151FF", "#FDE725FF"))+
    theme_bw(base_size=20)+
   theme(plot.title = element_text(hjust = 0.5))
```


Saving the workspace
```{r, eval=FALSE, include=FALSE}
save.image("RData/analise.CTC.ipiranga.RData")
```

```{r}
# par(mfcol=c(2,2))
# boxplot(dados$CTC,horizontal=TRUE, outline=TRUE)
# hist(dados$CTC, col="gray", xlab="CTC", main= "")
# par(mfcol=c(2,2))
# boxplot(ku$residuals,horizontal=TRUE, outline=TRUE)
# hist(ku$residuals, col="gray", xlab="Residuals RUK ~COV", main= "")
# par(mfcol=c(2,2))
# boxplot(ku.xy.sph$residuals,horizontal=TRUE, outline=TRUE)
# hist(ku.xy.sph$residuals, col="gray", xlab="Residuals RUK ~XY", main= "")
# par(mfcol=c(2,2))
# boxplot(kri.sph$residuals,horizontal=TRUE, outline=TRUE)
# hist(kri.sph$residuals, col="gray", xlab="Residuals ROK", main= "")
# par(mfcol=c(2,2))
# boxplot(cv.fit$residuals,horizontal=TRUE, outline=TRUE)
# hist(cv.fit$residuals, col="gray", xlab="Residuals RMLR", main= "")
```

The maps was save and ploted on QGis