
---
title: "Analysis K - area 2"
author: "Maiara Pusch"
---


The variables created throughout the code have been stored and can be loaded directly by the chunck below.
```{r}
#load("RData/analise.K.ipiranga.RData")
load("RData/potassio.RData")
```

installation of packages
```{r}
#install.packages("pacman")
pacman::p_load(georob, dplyr, tidyverse,pedometrics,raster,gstat,googlesheets,mapview,corrr,sf,robustbase,reshape,MASS,ggplot2,colormap,rgdal,caret,car)
```
      
Reading soil data
```{r}
dados = read.csv("../Data/Soil/soil_and_covariates_K_area2.csv")
dados=na.omit(dados)
names(dados)
```
```{r}
psych::describe(dplyr::select(dados,K))
```
  
```{r}
dados = dplyr::select(dados,-X)
```

When working with the integer values of the coordinates, the model displays errors in converting the values. In this way, subtract scans from the coordinates of their respective minimum values.
```{r}
dados$coordx= dados$x - min(dados$x)
dados$coordy= dados$y - min(dados$y)
```

Viewing points and area
```{r, error=T, fig.align='center', fig.cap="Fig 1. Pontos de amostragem com o valor de saturação por base"}
poly= shapefile("../Data/Boundary/22S.shp")
coordinates(dados)= ~x+y
crs(dados)= crs(poly)
#spplot(dat, zcol="K") 
mapview(poly, alpha.regions = 0.01, color = "red", map.types = c("Esri.WorldImagery")) + mapview(dados, zcol="K", legend=T)
```

```{r}
par(mfcol=c(2,2))
boxplot(dados$K, horizontal=TRUE, outline=TRUE, col="white")
hist(dados$K, col= "gray", xlab="Potássio", main=" K")
#hist(log(dados$K), col= "gray", xlab="Potássio", main="log(K)")
#qqnorm(dados$K)
```

In parentheses are the numbers corresponding to the soil classes.

*LVAe2.1(**6**), LVe1.1(**2**) e LVef1.1(**1**) received the number 10.

* PVAa3.1(**7**), LVAd3.1(**8**), LVAd2.1(**3**), LVAa3.1(**5**) received the number 20.

* RQoa4.1(**4**) e RQod4.1(**9**) received the number 30.
```{r}
names(dados)
```


```{r}
dados$SC[dados$SC=="1"]=10
dados$SC[dados$SC=="2"]=10
dados$SC[dados$SC== "6"]=10
dados$SC[dados$SC== "7"]=20
dados$SC[dados$SC== "8"]=20
dados$SC[dados$SC== "3"]=20
dados$SC[dados$SC== "5"]=20
dados$SC[dados$SC=="4"]=30
dados$SC[dados$SC=="9"]=30
dados$SC= as.factor(dados$SC)
dados$fields= as.factor(dados$fields)
dados=na.omit(dados)
str(dados)
```

 Check the relationship of soil types with potassium
```{r}
np= plyr::count(dados$SC)

ggplot(as.data.frame(dados), aes(SC, K)) +
   ylab("K (mmolc dm-3)")+
  xlab("TPS")+
  geom_boxplot(outlier.colour = "red") + 
  annotate("text",x=np$x, y=15, label = np$freq, colour= "red", size=4.5)+
theme_bw(base_size = 15)
``` 

Check the relationship of the fields with the K
```{r}
np= plyr::count(dados$fields)

ggplot(as.data.frame(dados), aes(fields, K)) +
  ylab("K (mmolc dm-3)")+
  xlab("Fields")+
  geom_boxplot(outlier.colour = "red") + 
  annotate("text",x=np$x, y=15, label = np$freq, colour= "red", size=4.5)+
theme_bw(base_size = 15)
``` 

correlation between variables
```{r}
cor= dados %>%
  as.data.frame() %>%
  dplyr::select(- SC, - fields, - coordx, - coordy)%>%
  correlate(method = "spearman", diagonal = 1, use = "pairwise.complete.obs")%>%
  mutate_if(is.numeric, round, 3) %>% 
   as.data.frame()
cor
```
 
 Variables that had correlations greater than **0.9** were selected  

```{r}
cor_above =cor %>%  
  gather(-term, key = "colname", value = "cor") %>% 
  filter(abs(cor) < 1 & abs(cor) >= 0.9) %>% 
  dplyr::select(term, colname, cor) %>% 
  distinct(cor, term,colname) %>% 
  arrange(cor) 
cor_above
```  

```{r}
names_above = cor_above$term
names_above
selected_var = cor %>% 
  dplyr::select(K, term) %>% 
  filter(term %in% names_above) %>% 
  arrange(K)
selected_var
```
```{r}
names(dados)
```


```{r}
reg.cov <- lm(K ~ ., data = dplyr::select(as.data.frame(dados), -green,-red,-NIR, -catch_area, -swir1, -swir2, - ECa0.375, - coordx, -coordy))

reg.cov.vif <- pedometrics::stepVIF(reg.cov, threshold = 10)
```

```{r}
summary(reg.cov.vif)
```



Selection of auxiliary variables by AKAIKE criterion (AIC)
```{r}
reg.aic= MASS::stepAIC(reg.cov.vif)
summary(reg.aic)
```

visualization of the behavior of multiple regression residuals as a function of the variables without colinearitye

```{r}
par(mfrow=c(2,2))
plot(reg.aic, which=c(1:6))
hist(reg.aic$residuals)
boxplot(reg.aic$residuals, horizontal = T)
```

```{r}
reg.aic$residuals
dados$residuo.aic= reg.aic$residuals
plot(gstat::variogram(residuo.aic ~1, data=dados, cutoff= 800, width=80, map=T), main=" residuals (K- Area 2)")
```
```{r}
max_dist = ceiling(max(dist(dados@coords)))
min_dist = ceiling(min(dist(dados@coords)))
plot(georob::sample.variogram(residuo.aic ~1, locations = ~x+y, data=dados, lag.dist.def= seq(0,max_dist/2, by= min_dist*1.4), xy.angle.def= c(0., 22.5, 67.5, 112.5, 157.5, 180.)), type="l", col=1:4, annotate=T);grid()
```


### Adjustment of the multivariate model according to auxiliary variables 

```{r}
plot(ku.sv <-sample.variogram(residuals(reg.aic),locations = dados@coords, lag.dist.def= seq(0,800, by=100), estimador="qn"), type="l", annotate=T, main="Resíduos da regressão")
```


Em busca do melhor parâmetro de suavidade
```{r}
#d= max(dist(dados@coords))/2

parametro =data.frame(v =  c(seq(0.2, 1, by=0.1),seq(1.5,4, by=0.5),6,8),
                      EM= NA,
                      MAE= NA,
                      RMSE = NA,
                      variance = NA,
                      nugget = NA,
                      scale=NA)
models= list()

for(i in 1:nrow(parametro)){
ku= georob::georob(K ~ ECa0.75 + elevation + fields, data = dados,  locations = ~ x + y,  variogram.model = "RMmatern",
                   param = c(variance= max(ku.sv$gamma)- min(ku.sv$gamma), nugget= min(ku.sv$gamma), scale= max_dist/2, nu= parametro$v[i]), 
                   psi.func = c("huber"),
                   control = control.georob(error.family.estimation = "long.tailed",
                                            error.family.cov.effects = "long.tailed"),
                   # aniso = default.aniso(f1 = 0.5, omega = 22.5),
                   # fit.aniso = default.fit.aniso(f1 = T, omega = TRUE),
                   #nlminb = control.nlminb(start= 0.00001, lower = c(0,0,0,0.5), upper=c(170,70,907,6.5)),
                   #nlminb= control.nlminb(lower=list(variance= 0, nugget= 0, scale=0,nu= parametro$v[i]), 
                   #upper=list(variance= var(dados$P), nugget= var(dados$P), scale= d, nu= parametro$v[i])),
                    fit.param = default.fit.param(variance=T, nugget = T, scale=T, nu=F))
models[[i]]= ku
parametro$EM[i]= mean(ku$residuals)
parametro$MAE[i]= mean(abs(ku$residuals))
parametro$RMSE[i]= sqrt(mean((ku$residuals)^2))
parametro$variance[i]= ku$variogram.object[[1]]$param[['variance']] 
parametro$nugget[i]= ku$variogram.object[[1]]$param[['nugget']] 
parametro$scale[i]= ku$variogram.object[[1]]$param[['scale']]
}
round(parametro,2)
#names(models)= parametro$v
#write.csv(parametro, "parametro_p_ku.csv")
```


```{r}
#ku= georob::georob(K ~ CH_1 + elevacao + talhoes, data = dados,  locations = ~ x + y,variogram.model = "RMmatern", param=c(variance=5, nugget=2, scale= 200, nu=0.5), fit.param = default.fit.param(variance=T, nugget = T, scale=T, nu=F), psi.func = c("huber"), verbose=2)

ku.sph= georob::georob(K ~ ECa0.75 + elevation + fields, data = dados,  locations = ~ x + y,variogram.model = "RMspheric", param=c(variance= max(ku.sv$gamma)- min(ku.sv$gamma), nugget= min(ku.sv$gamma), scale= max_dist/2), fit.param = default.fit.param(variance=T, nugget = T, scale=T), psi.func = c("huber"),control = control.georob(error.family.estimation = "long.tailed", error.family.cov.effects = "long.tailed"))

# ku.exp= georob::georob(K ~ CH_1 + elevacao + talhoes, data = dados,  locations = ~ x + y,variogram.model = "RMexp", param=c(variance=5, nugget=2,scale=300), fit.param = default.fit.param(variance=T, nugget = T, scale=T), psi.func = c("huber"))
```

```{r}
summary(models[[5]])
```
```{r}
plot(models[[5]],lag.dist.def=seq(0,max_dist/2, by= min_dist*1.4))
```

```{r}
summary(ku.sph)
```

```{r}
dados$residuo.ku= models[[2]]$residuals
plot(gstat::variogram(residuo.ku ~1, data=dados, cutoff= 800, width=80, map=T), main=" residuals (K- Area 2)")
```

Cross-validation (LOOCV)
lgn=T
```{r}
cv.ku = georob::cv(models[[5]], seed= 42, nset = 89, ncores=6)
#cv.ku1 =georob::cv(models[[6]], seed= 42, nset =89, ncores=6)
#cv.ku3 =georob::cv(models[[2]], seed= 42, nset =89, ncores=6)
cv.ku.sph =georob::cv(ku.sph, seed= 42, nset =89, ncores=6)
```


```{r}
cv.ku;cv.ku.sph
```

# ```{r}
# plot(cv.ku, main="Matern")
# plot(cv.ku.exp, main="Exponential")
# plot(cv.ku.sph, main="Spheric")
# ```


```{r,fig.align='center', fig.cap="Fig 7. Perfil da função logarítimica da verossimilhança restrita para o parâmetro alcance do modelo ajustado em função das covariáveis" }
scala= ku.sph$variogram.object[[1]]$param[4]
prfl.ku <- profilelogLik(ku.sph,values=data.frame(scale=seq(scala/2, max_dist/2, length.out = 30)))

#par(mfrow=c(1,3),mar=c(3, 2.5, 3, 1))
plot(loglik~scale, prfl.ku, type="l") #, main="RUK-6.5"
abline(v=ku.sph$variogram.object[[1]]$param[4])

plot(variance~scale, prfl.ku, ylim=c(0, max(variance)), type="l", main="K- Area2")
abline(h=models[[5]]$variogram.object[[1]]$param[1], lty=2)

plot(nugget~scale, prfl.ku, ylim=c(0, max(nugget)), type="l")
abline(h=models[[5]]$variogram.object[[1]]$param[3], lty=2)
```



```{r}
plot(models[[5]], lag.dist.def=seq(0,1000, by=100), max.lag=1100, estimator="ch", xlab ="Distance", ylab = "Semivariance", main="ku", type="p",annotate=T)
plot(ku.sph, lag.dist.def=seq(0,1000, by=100), max.lag=1100, estimator="qn", xlab ="Distance", ylab = "Semivariance", main="ku", type="p",add=T, col="red")
#lines(ku.sph, col="red")
#lines(ku.exp, col="blue")
```

### Adjustment of the multivariate model according to coordinates  
```{r}
reg.xy= lm(K ~ coordx + coordy, dados)
plot(ku.xy.sv <-sample.variogram(residuals(reg.xy),locations = dados@coords, lag.dist.def= seq(0,600, by=60), estimador="qn"), type="p", annotate=T)
```
Em busca do melhor parâmetro de suavidade
```{r}
parametro.xy =data.frame(v = c(seq(0.2, 1, by=0.1),seq(1.5,4, by=0.5),6,8),
                      EM= NA,
                      MAE= NA,
                      RMSE = NA,
                      variance = NA,
                      nugget = NA,
                      scale=NA)
models.xy= list()

for(i in 1:nrow(parametro.xy)){
ku.xy= georob::georob(K ~ coordx +coordy, data = dados,  locations = ~ x + y,  variogram.model = "RMmatern",
                   param = c(variance= max(ku.xy.sv$gamma)- min(ku.xy.sv$gamma), nugget= min(ku.xy.sv$gamma), scale= max_dist/3, nu= parametro.xy$v[i]), 
                   psi.func = c("huber"),
                   control = control.georob(error.family.estimation = "long.tailed",
                                            error.family.cov.effects = "long.tailed"),
                   # aniso = default.aniso(f1 = 0.7, omega = 95.),
                   # fit.aniso = default.fit.aniso(f1 = F, omega = TRUE),
                   #nlminb = control.nlminb(start= 0.00001, lower = c(0,0,0,0.5), upper=c(170,70,907,6.5)),
                   #nlminb= control.nlminb(lower=list(variance= 0, nugget= 0, scale=0,nu= parametro$v[i]), 
                   #upper=list(variance= var(dados$P), nugget= var(dados$P), scale= d, nu= parametro$v[i])),
                    fit.param = default.fit.param(variance=T, nugget = T, scale=T, nu=F))
models.xy[[i]]= ku.xy
parametro.xy$EM[i]= mean(ku.xy$residuals)
parametro.xy$MAE[i]= mean(abs(ku.xy$residuals))
parametro.xy$RMSE[i]= sqrt(mean((ku.xy$residuals)^2))
parametro.xy$variance[i]= ku.xy$variogram.object[[1]]$param[['variance']] 
parametro.xy$nugget[i]= ku.xy$variogram.object[[1]]$param[['nugget']] 
parametro.xy$scale[i]= ku.xy$variogram.object[[1]]$param[['scale']]
}
round(parametro.xy,2)
```
```{r}
plot(models.xy[[6]],lag.dist.def=seq(0,max_dist/2, by= min_dist*1.4), estimator="ch")
#plot(ku.sph,lag.dist.def=seq(0,max_dist/2, by= min_dist*1.4), ylim=c(0,150), estimator="ch", add=T) 
```

```{r}
# ku.xy = georob::georob(K ~ coordx + coordy, data = dados,  locations = ~ x + y, variogram.model = "RMmatern", param=c(variance=6, nugget=1, scale= 300, nu=0.5), fit.param = default.fit.param(variance=T, nugget = T, scale=T, nu=F), psi.func = c("huber"), verbose=1)
# 
ku.xy.sph = georob::georob(K ~ coordx + coordy, data = dados,  locations = ~ x + y, variogram.model = "RMspheric", param=c(variance= max(ku.xy.sv$gamma)- min(ku.xy.sv$gamma), nugget= min(ku.xy.sv$gamma), scale= max_dist/3), fit.param = default.fit.param(variance=T, nugget = T, scale=T),psi.func = c("huber"),control = control.georob(error.family.estimation = "long.tailed",
                                            error.family.cov.effects = "long.tailed"))
# 
# ku.xy.exp = georob::georob(K ~ coordx + coordy, data = dados,  locations = ~ x + y, variogram.model = "RMexp", param=c(variance=6, nugget=2, scale= 300), fit.param = default.fit.param(variance=T, nugget = T, scale=T),psi.func = c("huber"), verbose=1)
```

```{r}
summary(models.xy[[6]])
```
```{r}
summary(ku.xy.sph)
```


Cross-validation  (LOOCV)
```{r}
cv.xy = georob::cv(models.xy[[6]], seed= 42, nset =89, ncores=6,control=control.georob(initial.param=FALSE))
cv.xy.sph = georob::cv(ku.xy.sph, seed= 42, nset =89, ncores=6)
#cv.xy.exp = georob::cv(ku.xy.exp, seed= 42, nset =95, ncores=6)
```

```{r}
cv.xy;cv.xy.sph
```

```{r}
# plot(cv.xy.sph, main="Spheric")
```


```{r,fig.align='center', fig.cap="Fig 7. Perfil da função logarítimica da verossimilhança restrita para o parâmetro alcance do modelo ajustado em função das covariáveis" }
scala= ku.xy.sph$variogram.object[[1]]$param[4]
prfl.ku.xy <- profilelogLik(ku.xy.sph,values=data.frame(scale=seq(scala/2, max_dist/2, length.out = 30)))

#par(mfrow=c(1,3),mar=c(3, 2.5, 3, 1))
plot(loglik~scale, prfl.ku.xy, type="l") #, main="RUK-6.5"
abline(v=ku.xy.sph$variogram.object[[1]]$param[4])

plot(variance~scale, prfl.ku.xy, ylim=c(0, max(variance)), type="l", main="K- Area2")
abline(h=ku.xy.sph$variogram.object[[1]]$param[1], lty=2)

plot(nugget~scale, prfl.ku.xy, ylim=c(0, max(nugget)), type="l")
abline(h=ku.xy.sph$variogram.object[[1]]$param[3], lty=2)
```


### Univariate model adjustment 

```{r} 
reg.kri= lm(K ~1, dados)
plot(kri.sv <-sample.variogram(residuals(reg.kri),locations = dados@coords, lag.dist.def= seq(0,600, by=100), estimador="qn"), type="p", annotate=T)
```

Em busca do melhor parâmetro de suavidade
```{r}
parametro.kri =data.frame(v = c(seq(0.2, 1, by=0.1),seq(1.5,4, by=0.5),6,8),
                      EM= NA,
                      MAE= NA,
                      RMSE = NA,
                      variance = NA,
                      nugget = NA,
                      scale=NA)
models.kri= list()

for(i in 1:nrow(parametro.kri)){
kri= georob::georob(K ~ 1, data = dados,  locations = ~ x + y,  variogram.model = "RMmatern",
                   param = c(variance= max(kri.sv$gamma)- min(ku.sv$gamma), nugget= min(kri.sv$gamma), scale= max_dist/3, nu= parametro.kri$v[i]), 
                   psi.func = c("huber"),
                   control = control.georob(error.family.estimation = "long.tailed",
                                            error.family.cov.effects = "long.tailed"),
                   # aniso = default.aniso(f1 = 0.7, omega = 95.),
                   # fit.aniso = default.fit.aniso(f1 = F, omega = TRUE),
                   #nlminb = control.nlminb(start= 0.00001, lower = c(0,0,0,0.5), upper=c(170,70,907,6.5)),
                   #nlminb= control.nlminb(lower=list(variance= 0, nugget= 0, scale=0,nu= parametro$v[i]), 
                   #upper=list(variance= var(dados$P), nugget= var(dados$P), scale= d, nu= parametro$v[i])),
                    fit.param = default.fit.param(variance=T, nugget = T, scale=T, nu=F))
models.kri[[i]]= kri
parametro.kri$EM[i]= mean(kri$residuals)
parametro.kri$MAE[i]= mean(abs(kri$residuals))
parametro.kri$RMSE[i]= sqrt(mean((kri$residuals)^2))
parametro.kri$variance[i]= kri$variogram.object[[1]]$param[['variance']] 
parametro.kri$nugget[i]= kri$variogram.object[[1]]$param[['nugget']] 
parametro.kri$scale[i]= kri$variogram.object[[1]]$param[['scale']]
}
round(parametro.kri,2)
#names(models)= parametro$v
#write.csv(parametro, "parametro_p_ku.csv")
```

```{r}
# kri=  georob::georob(K ~ 1, data = dados,  locations = ~ x + y,variogram.model = "RMmatern",param=c(variance=6, nugget=2, scale= 350, nu= 0.5), fit.param = default.fit.param(variance=T, nugget = T, scale=T, nu=F),psi.func = c("huber"))
# 
kri.sph=  georob::georob(K ~ 1, data = dados,  locations = ~ x + y,variogram.model = "RMsph",param=c(variance=6, nugget=2, scale= 350), fit.param = default.fit.param(variance=T, nugget = T, scale=T),psi.func = c("huber"),control = control.georob(error.family.estimation = "long.tailed",
                                            error.family.cov.effects = "long.tailed"))
# 
# kri.exp=  georob::georob(K ~ 1, data = dados,  locations = ~ x + y,variogram.model = "RMexp",param=c(variance=6, nugget=2, scale= 350), fit.param = default.fit.param(variance=T, nugget = T, scale=T),psi.func = c("huber"))
```

```{r}
summary(models.kri[[7]])
```

```{r}
summary(kri.sph)
```

```{r}
plot(models.kri[[7]],lag.dist.def=seq(0,max_dist/2, by= min_dist*1.4), estimator="ch", ylim=c(0,10))
plot(kri.sph,lag.dist.def=seq(0,max_dist/2, by= min_dist*1.4), estimator="ch", add=T) 
```

cross validation (LOOCV)
```{r, warning=T , error=T}
cv.kri = georob::cv(models.kri[[7]], seed= 42, nset =89, ncores=6,control=control.georob(initial.param=FALSE))
#cv.kri1 = georob::cv(models.kri[[6]], seed= 42, nset =89, ncores=6,control=control.georob(initial.param=FALSE))
cv.kri.sph = georob::cv(kri.sph, seed= 42, nset =89, ncores=6)
#cv.kri.exp = georob::cv(kri.exp, seed= 42, nset =95, ncores=6,control=control.georob(initial.param=FALSE))
```

```{r}
cv.kri;cv.kri.sph
```


```{r,fig.align='center', fig.cap="Fig 7. Perfil da função logarítimica da verossimilhança restrita para o parâmetro alcance do modelo ajustado em função das covariáveis" }
scala= kri.sph$variogram.object[[1]]$param[4]
prfl.kri <- profilelogLik(kri.sph,values=data.frame(scale=seq(scala/2, max_dist/2, length.out = 30)))

#par(mfrow=c(1,3),mar=c(3, 2.5, 3, 1))
plot(loglik~scale, prfl.kri, type="l") #, main="RUK-6.5"
abline(v=kri.sph$variogram.object[[1]]$param[4])

plot(variance~scale, prfl.kri, ylim=c(0, max(variance)), type="l", main="K- Area2")
abline(h=models.kri[[1]]$variogram.object[[1]]$param[1], lty=2)

plot(nugget~scale, prfl.kri, ylim=c(0, max(nugget)), type="l")
abline(h=models.kri[[1]]$variogram.object[[1]]$param[3], lty=2)
```


```{r}
print(plot(kri.sph, lag.dist.def=seq(0,600, by=100), max.lag=1100, estimator="ch", xlab ="Distance", ylab = "Semivariance", type="p",annotate=T, main="kriging"))
#lines(kri.sph, col="red")
#lines(kri.exp, col = "blue")
```

```{r}
#plot(cv.kri.sph, main="Spheric")
```

Visualization of semivariogram all models
```{r}
print(plot(kri.sph, lag.dist.def=seq(0,600, by=100),  estimator="ch", xlab ="Distance", ylab = "Semivariance", type="p", cex.lab=1.5, cex.axis=1), title="CTC");grid()
print(plot(ku.xy.sph, lag.dist.def=seq(0,600, by=100),  estimator="ch", xlab ="Distance", ylab = "Semivariance", type="p",add=T, col="blue", cex.lab=1.5, cex.axis=1))
print(plot(ku.sph, lag.dist.def=seq(0,600, by=100),  estimator="ch", xlab ="Distance", ylab = "Semivariance", type="p",add=T, col="red", cex.lab=1.5, cex.axis=1))
title("K (mmolc dm-3) - Area 2")
```

Cross-validation (LOOCV) deterministic model IDW
```{r}
cv.idw=gstat::krige.cv(K ~ 1, dados, nfold = 90)# validação cruzada
cv.idw=as.data.frame(cv.idw)# transforma para data.frame
statistics.idw <- c(
        me = mean(cv.idw$observed - cv.idw$var1.pred ),
        medme = median(cv.idw$observed - cv.idw$var1.pred ),
        mae = mean(abs(cv.idw$observed - cv.idw$var1.pred)),
        rmse = sqrt( mean((cv.idw$observed - cv.idw$var1.pred )^2 ) ),
        nse2 =1- sum((cv.idw$observed - cv.idw$var1.pred)^2)/ sum((cv.idw$observed- mean(cv.idw$observed))^2),
        nse1 =1- sum(abs(cv.idw$observed - cv.idw$var1.pred))/ sum(abs(cv.idw$observed- mean(cv.idw$observed))))
```

```{r}
# plot(cv.idw$observed ~cv.idw$var1.pred)
# lmidw=lm(cv.idw$observed ~cv.idw$var1.pred)
# abline(lmidw)
```

Cross-validation  (LOOCV) for the regression model according to auxiliary variables

* The dat variable was added, only the information used in cross-validation, in order to facilitate calculations.
* A data frame was created that would store the metrics
* The average of the metrics of each fold was performed

```{r}
install.packages("dplyr", dependencies = T)
names(dados)
dat = dplyr::select(as.data.frame(dados),-green,-red,-NIR, -catch_area, -swir1, -swir2, - ECa0.375, - coordx, -coordy, residuo.aic, residuo.ku)
dat= as.data.frame(dados)
```


```{r}
model= MASS::rlm(K ~ ECa0.75 + elevation + fields, data=dat, psi = psi.huber, k2= 2, escale.est= "Huber")

#data <- model.frame(model)
idx  <- seq(1, nrow(dat), 1)
#data <- cbind(data, idx)
obs  <- numeric()
pred <- numeric()
pev  <- numeric()
    # run cross-validation
set.seed(43)
for (i in 1:nrow(dat)) {
      cv.fit     <- MASS::rlm(formula(model), subset = idx[-i], data = dat,psi = psi.huber, k=2, escale.est= "Huber")
      cv.pred    <- predict(cv.fit, dat[i, ], se.fit = TRUE, interval =c("prediction"), type= c("response"))
      obs[i]     <- dat[i, 1]
      pred[i]    <- cv.pred$fit
  
      # standard deviation of the predicted mean value of Y
      # sd.mean[i] <- cv.pred$se.fit
      # standard deviation of a predicted values of an individual observation
      # also known as prediction error variance
      pev[i] <- (sqrt(1 + c(cv.pred$se.fit/cv.pred$residual.scale) ^ 2) *
                   cv.pred$residual.scale) ^ 2
}

pev2= (cv.pred$se.fit^2) + (cv.pred$residual.scale^2)

statistics.predict <- c(
        me = mean(obs - pred),
        medme = median(obs - pred),
        mae = mean(abs(obs - pred)),
        rmse = sqrt(mean((obs - pred)^2)),
        nse2 =1-sum((obs - pred)^2)/
        sum((obs - mean(obs))^2),
        nse1 =1-(sum(abs(obs - pred))/
        sum(abs(obs - mean(obs)))),
        # Compara as diferenças do erro ao quadrado pela variação dos erros de predição    
        msse =mean((obs - pred)^2/pev),
        medsse =median((obs - pred)^2/pev))

msdr2 =mean((obs - pred)^2/pev2)
statistics.predict;msdr2
```

```{r}
# par(mfcol=c(2,2))
# boxplot(cv.fit$residuals, horizontal=TRUE, outline=TRUE)
# hist(cv.fit$residuals, col= "gray")
```

```{r}
#r2= hydroGOF::br2(cv.xy.sph$pred$pred, cv.xy.sph$pred$data)
```

model basead in the mean

```{r}
model1= lm(K ~ 1, data=dat)

#data <- model.frame(model)
idx1  <- seq(1, nrow(dat), 1)
#data <- cbind(data, idx)
obs1  <- numeric()
pred1 <- numeric()
pev1  <- numeric()
   # sd.mean <- numeric()
    # sigma   <- numeric()
    # run cross-validation
for (i in 1:nrow(dat)) {
      cv.fit1     <- lm(formula(model1), subset = idx1[-i], data = dat)
      cv.pred1    <- predict(cv.fit1, dat[i, ], se.fit = TRUE, interval =c("prediction"), type= c("response"))
      obs1[i]     <- dat[i, 1]
      pred1[i]    <- cv.pred1$fit
  
      # standard deviation of the predicted mean value of Y
      # sd.mean[i] <- cv.pred$se.fit
      # standard deviation of a predicted values of an individual observation
      # also known as prediction error variance
      pev1[i] <- (sqrt(1 + c(cv.pred1$se.fit/cv.pred1$residual.scale) ^ 2) *
                   cv.pred1$residual.scale) ^ 2
  
}

pev2= (cv.pred1$se.fit^2) + (cv.pred1$residual.scale^2)

statistics.predict.mean <- c(
        me = mean(obs1 - pred1),
        medme = median(obs1 - pred1),
        
        mae = mean(abs(obs1 - pred1)),
        
        rmse = sqrt(mean((obs1 - pred1)^2)),
        
        nse2 =1-sum((obs1 - pred1)^2)/
        sum((obs1 - mean(obs1))^2),

        nse1 =1-(sum(abs(obs1 - pred1))/
        sum(abs(obs1 - mean(obs1)))),
        # Compara as diferenças do erro ao quadrado pela variação dos erros de predição    
        msse =mean((obs1 - pred1)^2/pev1),
        medsse =median((obs1 - pred1)^2/pev1))

msdr2 =mean((obs1 - pred1)^2/pev2)
statistics.predict.mean
```



```{r}
statistics.kri <- c(
        me = mean(cv.kri.sph$pred$data - cv.kri.sph$pred$pred),
        medme = median(cv.kri.sph$pred$data - cv.kri.sph$pred$pred),
        mae = mean(abs(cv.kri.sph$pred$data - cv.kri.sph$pred$pred)),
        rmse = sqrt( mean((cv.kri.sph$pred$data - cv.kri.sph$pred$pred)^2)),
        nse2=1-sum((cv.kri.sph$pred$data - cv.kri.sph$pred$pred)^2)/
        sum((cv.kri.sph$pred$data- mean(cv.kri.sph$pred$data))^2),
        nse1=1-sum(abs(cv.kri.sph$pred$data - cv.kri.sph$pred$pred))/
        sum(abs(cv.kri.sph$pred$data- mean(cv.kri.sph$pred$data))),
        msse= mean(((cv.kri.sph$pred$data - cv.kri.sph$pred$pred)/cv.kri.sph$pred$se)^2))
```

```{r}
statistics.xy <- c(
        me = mean(cv.xy.sph$pred$data - cv.xy.sph$pred$pred),
        medme = median(cv.xy.sph$pred$data - cv.xy.sph$pred$pred),
        mae = mean(abs(cv.xy.sph$pred$data - cv.xy.sph$pred$pred)),
        rmse = sqrt( mean((cv.xy.sph$pred$data - cv.xy.sph$pred$pred)^2)),
        nse2=1-sum((cv.xy.sph$pred$data - cv.xy.sph$pred$pred)^2)/
        sum((cv.xy.sph$pred$data- mean(cv.xy.sph$pred$data))^2),
        nse1=1-sum(abs(cv.xy.sph$pred$data - cv.xy.sph$pred$pred))/
        sum(abs(cv.xy.sph$pred$data- mean(cv.xy.sph$pred$data))),
        msse= mean(((cv.xy.sph$pred$data - cv.xy.sph$pred$pred)/cv.xy.sph$pred$se)^2))
```

```{r}
statistics.ku <- c(
        me = mean(cv.ku.sph$pred$data - cv.ku.sph$pred$pred),
        medme = median(cv.ku.sph$pred$data - cv.ku.sph$pred$pred),
        mae = mean(abs(cv.ku.sph$pred$data - cv.ku.sph$pred$pred)),
        rmse = sqrt(mean((cv.ku.sph$pred$data - cv.ku.sph$pred$pred)^2)),
        nse2=1-sum((cv.ku.sph$pred$data - cv.ku.sph$pred$pred)^2)/
        sum((cv.ku.sph$pred$data- mean(cv.ku.sph$pred$data))^2),
        nse1=1-sum(abs(cv.ku.sph$pred$data - cv.ku.sph$pred$pred))/
        sum(abs(cv.ku.sph$pred$data- mean(cv.ku.sph$pred$data))),
        msse= mean(((cv.ku.sph$pred$data - cv.ku.sph$pred$pred)/cv.ku.sph$pred$se)^2))
```

```{r}
me=rbind(statistics.kri, statistics.xy, statistics.ku)
statistics.idw;me;statistics.predict
```

Create the interpolation grid 
```{r}
grid = read.csv("../Data/grid/grid_ipiranga.csv")
str(grid)
grid= dplyr::select(grid, -X)
grid= dplyr::rename(grid, green =b3, red=b4, NIR=b5, GC=CG,HC = CH, ECa0.375=CH_0.5m,ECa0.75 =CH_1,elevation =elevacao, swir1=sw1,swir2 =sw2, fields=talhoes, SC=TPS)
coordinates(grid)= ~x+y

grid$SC[grid$SC=="1"]=10
grid$SC[grid$SC=="2"]=10
grid$SC[grid$SC== "6"]=10
grid$SC[grid$SC== "7"]=20
grid$SC[grid$SC== "8"]=20
grid$SC[grid$SC== "3"]=20
grid$SC[grid$SC== "5"]=20
grid$SC[grid$SC=="4"]=30
grid$SC[grid$SC=="9"]=30

grid= as(grid, "SpatialPixelsDataFrame")
grid$fields= as.factor(grid$fields)
grid$coordx= grid$x - min(grid$x)
grid$coordy = grid$y - min(grid$y)
grid$SC= as.factor(grid$SC)
grid$fields= as.factor(grid$fields)
grid=na.omit(grid)
str(grid)
```

prediction by KU according to auxiliary variables and visualization of the prediction map 

```{r}
map.ku.cov <- predict(ku.sph, newdata= grid, control=control.predict.georob(extended.output=TRUE))
sp::gridded(map.ku.cov)= TRUE
sp::spplot(map.ku.cov, c("pred"), main="Robust Universal Kriging prediction", scales=list(draw=TRUE))
summary(ku.sph)
```

prediction by KU according to the coordinates and visualization of the prediction map

```{r }
map.ku.xy <- predict(ku.xy.sph, newdata= grid, control=control.predict.georob(extended.output=TRUE))
sp::gridded(map.ku.xy)= TRUE
sp::spplot(map.ku.xy, c("pred"), main="Robust Universal Kriging prediction", scales=list(draw=TRUE)) 
summary(kri.sph)
```

Prediction by OK and visualization of the prediction map

```{r}
map.kri <- predict(kri.sph, newdata= grid, control=control.predict.georob(extended.output=TRUE))
sp::gridded(map.kri)= TRUE
sp::spplot(map.kri, c("pred"), main="Robust Ordinary Kriging prediction", scales=list(draw=TRUE))
```


Deterministic model prediction and prediction map visualization
```{r}
proj4string(dados)= CRS(proj4string(grid))
map.idw= gstat::idw(K ~1, dados, grid)
sp::spplot(map.idw, c("var1.pred"),main="IDW prediction", scales=list(draw=TRUE))
```


Prediction of the regression model and prediction map visualization
```{r}
grid.reg = as.data.frame(grid)
#grid.reg= na.omit(grid.reg)
map.reg =  predict(model, newdata= grid.reg, type = c("response"), se.fit=T)
map.reg = as.data.frame(map.reg)
map.reg$x = grid.reg$x
map.reg$y = grid.reg$y
names(map.reg)
map.reg= map.reg[,c(5,6,1,2)]#x, y,fit, se.fit
#map.reg=dplyr::select(map.reg, x, y,fit, se.fit)
map.reg=rasterFromXYZ(map.reg)
sp::spplot(map.reg, c("fit"))
sp::spplot(map.reg, c("se.fit"))
#install.packages("dplyr", force=T)
```


Selects the predicted values of each method. Then we group in a data frame so that I calculate the densities, it is necessary that the memos are grouped into a single column, for this we use the melt function.
```{r}
ROK= (cv.kri.sph$pred$pred)
RUK_coord= (cv.xy.sph$pred$pred)
RUK_covars= (cv.ku.sph$pred$pred)
IDW= (cv.idw$var1.pred)
RMLR= (pred)
OBS= dados$K
#df=cbind(kri.pred, obs,xy.pred)
df= cbind(IDW, RMLR, ROK, RUK_coord, RUK_covars, OBS)
df = as.data.frame(df)
df1=reshape::melt(df, variable.series = "Metodos")
df1 = dplyr::rename(df1, Methods= variable)
names(df1)
names(df1)= c("Methods", "value")
#write.csv(df1, "../dados/df1.k_ipiranga.csv")
```

Compare the similarity between two distributions by means of the kolmorogov-smirnov test
```{r}
# Kolmorogv-smirnov
obs.kri= ks.test(OBS, ROK)
obs.ku= ks.test(OBS, RUK_covars)
obs.ku_xy= ks.test(OBS, RUK_coord)
obs.idw= ks.test(OBS, IDW)
obs.reg= ks.test(OBS, RMLR)
```

Density of predicted values in cross-validation

```{r}
ggplot(df1, aes(x= value, y= Methods, fill= Methods) )+
  ggridges::geom_density_ridges(scale=3, alpha=1, show.legend = F)+
  labs(title = "K (mmolc dm-3) - Area 2") +
  scale_fill_manual(values=c("#440154FF", "#414487FF", "#2A788EFF", "#22A884FF", "#7AD151FF", "#FDE725FF"))+
  theme_bw(base_size=15)+
   theme(plot.title = element_text(hjust = 0.5))
library(ggplot2)
```


```{r}
par(mfcol=c(2,2))
boxplot(dados$K,horizontal=TRUE, outline=TRUE)
hist(dados$K, col="gray", xlab="K", main= "")
par(mfcol=c(2,2))
boxplot(kri.sph$residuals,horizontal=TRUE, outline=TRUE)
hist(kri.sph$residuals, col="gray", xlab="Residuals ROK", main= "")
par(mfcol=c(2,2))
boxplot(ku.xy.sph$residuals,horizontal=TRUE, outline=TRUE)
hist(ku.xy.sph$residuals, col="gray", xlab="Residuals RUK_coord", main= "")
par(mfcol=c(2,2))
boxplot(cv.fit$residuals,horizontal=TRUE, outline=TRUE)
hist(cv.fit$residuals, col="gray", xlab="Residuals RMLR", main= "")
par(mfcol=c(2,2))
boxplot(ku.sph$residuals,horizontal=TRUE, outline=TRUE)
hist(ku.sph$residuals, col="gray", xlab="Residuals RUK_covars", main= "")

```

The maps was save and ploted on QGis

# ```{r}
# mapaRaster = stack(map.reg)
# proj4string(mapaRaster) = proj4string(poly)
# writeRaster(mapaRaster,
#             filename = paste0("../../Area2/Data/mapas/k/rmlr/",names(mapaRaster)),
#             format= "GTiff",
#             bylayer=T,
#             overwrite=T)
# ```
# 
# ```{r eval=FALSE, include=FALSE}
# mapaRaster = raster(map.idw)
# proj4string(mapaRaster) = proj4string(poly)
# writeRaster(mapaRaster,
#             filename = paste0("../Data/mapas/k/idw/",names(mapaRaster)),
#             format= "GTiff",
#             bylayer=T,
#             overwrite=F)
# ```
# 
# Salvar os mapas gerados
# ```{r eval=FALSE, include=FALSE}
# mapaRaster = stack(map.kri)
# proj4string(mapaRaster) = proj4string(poly)
# writeRaster(mapaRaster,
#             filename = paste0("../Data/mapas/k/rok/",names(mapaRaster)),
#             format= "GTiff",
#             bylayer=T,
#             overwrite=T)
# ```
# 
# Salvar os mapas
# ```{r eval=FALSE, include=FALSE}
# mapaRaster = stack(map.ku.xy)
# proj4string(mapaRaster) = proj4string(poly)
# writeRaster(mapaRaster,
#             filename = paste0("../Data/mapas/k/rukcoord/",names(mapaRaster)),
#             format= "GTiff",
#             bylayer=T,
#             overwrite=T)
# ```
# 
# Salvar os mapas
# ```{r eval=FALSE, include=FALSE}
# mapaRaster = stack(map.ku.cov)
# proj4string(mapaRaster) = proj4string(poly)
# writeRaster(mapaRaster,
#             filename = paste0("../Data/mapas/k/rukcovars/",names(mapaRaster)),
#             format= "GTiff",
#             bylayer=T,
#             overwrite=T)
# ```

```{r}
par(mfrow=c(2,3))
plot(loglik~scale, prfl.kri, type="l", main="ROK P-Area2") #, main="RUK-6.5"
abline(v=models.kri[[11]]$variogram.object[[1]]$param[4], lty=2)

plot(variance~scale, prfl.kri, ylim=c(0, max(variance)), type="l", main="ROK P- Area2")
abline(h=models.kri[[11]]$variogram.object[[1]]$param[1], lty=2)

plot(nugget~scale, prfl.kri, ylim=c(0, max(nugget)), type="l")
abline(h=models.kri[[11]]$variogram.object[[1]]$param[3], lty=2)


plot(loglik~scale, prfl.ku.xy, type="l", main="RUKcoord P-Area2") #, main="RUK-6.5"
abline(v=ku.xy.sph$variogram.object[[1]]$param[4], lty=2)

plot(variance~scale, prfl.ku.xy, ylim=c(0, max(variance)), type="l", main="RUKcoord P- Area2")
abline(h=ku.xy.sph$variogram.object[[1]]$param[1], lty=2)

plot(nugget~scale, prfl.ku.xy, ylim=c(0, max(nugget)), type="l")
abline(h=ku.xy.sph$variogram.object[[1]]$param[3], lty=2)
```

```{r}
save.image("potassio.RData")
```



